% %--------------------------
% %	CONFIGURATION
% %--------------------------
\documentclass[11pt,a4paper]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{black}
\definecolor{firstnamecolor}{rgb}{0,0,0}

% Basic packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scale=0.85]{geometry}
\usepackage[dvipsnames]{xcolor}
\definecolor{DarkBlue}{RGB}{0, 0, 150} % or tweak as needed
\usepackage[colorlinks=true, urlcolor=DarkBlue, linkcolor=DarkBlue]{hyperref}

\usepackage{microtype} % For better typography

% Configure font settings
\renewcommand{\rmdefault}{ppl} % Use Palatino font
\renewcommand{\sfdefault}{phv} % Use Helvetica font for sans-serif text
\renewcommand*{\namefont}{\fontsize{26}{18}\mdseries}

% Configure microtype
\microtypesetup{expansion=false}

% Load sensitive information
\input{../../personal_info.tex}

% Title document
\title{Curriculum Vitae}

% %--------------------------

\begin{document}
\makecvtitle

\section*{Introduction}
I am an curious Data Scientist with 6 years of experience applying ML across many industries. I have previous experience as a data science researcher building computer vision models in radiotherapy for cancer treatment. I have a strong mathematical background and perfect GPA. After some time in industry, I am excited to return to academia to further my learning and contribute to AI research.


% Include modular sections

\section{Selected Work Experience}
\input{../../sections/work_experience/raysearch/summary.tex}
\input{../../sections/work_experience/valcon/summary.tex}

\input{../../sections/education/summary.tex}
\input{../../sections/other/iris/summary.tex}
\input{../../sections/other/other.tex}

\newpage
\section{Detailed Work Experience}

\phantomsection\label{sec:signum}
\cventry{2024--Present}{Data Scientist and Project Manager}{Signum Life Science}{Copenhagen}{}{
    At Signum, I lead development on Kwarts, a next-best-action engine for pharmaceutical sales. I have extended the system with explainable AI features, supported its commercialisation, and ensured scalability on AWS. I also maintain our pharmaceutical price forecasting model for Denmark's biweekly auctions. In addition, I organised a week-long internal hackathon with 40 participants, which fostered innovation and produced several new prototypes.
}{}

\phantomsection\label{sec:valcon}
\cventry{2022--2024}{Principal Data Scientist}{Valcon}{Copenhagen}{}{
    Led data science projects across pharma, energy, IoT, and manufacturing, while mentoring colleagues and shaping internal practices through xAI and Git trainings. I regularly presented to non-technical stakeholders, strengthening my ability to translate complex ideas clearly. As lead data scientist, I designed and deployed a real-time deep neural network with a custom training pipeline for a challenging natural-language, multi-label prediction task. I received the "Valcon People's Choice Award" for exemplary work, leadership, and scientific curiosity.
}{}

\phantomsection\label{sec:valtech}
\cventry{2021--2022}{Data Scientist}{Valtech}{Copenhagen}{}{}{}

\phantomsection\label{sec:raysearch}
\cventry{2019--2021}{Researcher within Data Science}{RaySearch Laboratories}{Stockholm}{}{
    At RaySearch Laboratories, I worked on automating radiotherapy planning using deep learning, probabilistic modelling, and multi-objective optimisation. I built a pipeline that extracted anatomical features from 3D CT scans with autoencoders, identified similar patients, and predicted dose distributions with sparse Gaussian processes, enabling personalised, data-driven treatment planning. I also redesigned lexicographic optimisation algorithms to better reflect clinical decision hierarchies, collaborating closely with physicists and oncologists to ensure clinical relevance.
}{}

\section{Other Detailed Experience}
\phantomsection\label{sec:iris}
\cventry{2025-Present}{Solo Project}{Project iris}{}{}{
    In this personal project I am building an end-to-end computer vision system that makes e-commerce product images interactive. Using YOLOv8 and OpenCLIP, the pipeline detects and embeds items to enable intelligent product linking. It includes a FastAPI backend, MongoDB, Qdrant for vector search, and a custom Chromium plug-in that overlays clickable links on images in real time. The project has been a valuable exercise in fine-tuning deep learning models and full-stack ML engineering.
}{}

\end{document}
