\phantomsection\label{sec:valcon}
\cventry{2022--2024}{Principal Data Scientist}{Valcon}{Copenhagen}{}{
    Functioning as the lead data scientist on a variety of projects in industries such as pharmaceuticals, pension, energy transmission, IoT systems, disaster recovery, and manufacturing. A large part of my role at Valcon consists of training junior colleagues. This, among other things, involves showing how to properly architect data science solutions to make for a maintainable and robust solution as well as teaching data science practices. I have initiated and given internal trainings in explainability for machine learning and Git and have had a central coordinating role in the data science team. Projects at Valcon always include a business angle, and presenting findings of advanced research projects to non-technical clients has helped me develop presentation skills for which I have received much positive feedback. One recent project involved extracting and analysing a large IoT dataset. The data came from an ice cream manufacturing line where we wished to explain the variability in operator productivity. This was done with the use of clustering of operators to gain an understanding of the differences in modes of operation. In addition, we developed a set of dashboards hosted together with the data platform in a docker container for easy portability. Read more here. My current project involves training a real-time deep neural network with an advanced custom training pipeline and modular architecture. The training data consists of natural-language and high dimensional multi-class labels which makes for a challenging prediction problem. I am the lead data scientist and architect of the solution and responsible for implementing the end-to-end production ready pipeline. I am leading a small dynamic team of data engineers and data scientists. I was recently awarded the Valcon People's Choice award for exemplary work, leadership, team spirit and scientific curiosity.
}{}