% %--------------------------
% %	CONFIGURATION
% %--------------------------
\documentclass[11pt,a4paper]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{black}
\definecolor{firstnamecolor}{rgb}{0,0,0}

% Basic packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scale=0.7]{geometry}
\usepackage[dvipsnames]{xcolor}
\definecolor{DarkBlue}{RGB}{0, 0, 150} % or tweak as needed
\usepackage[colorlinks=true, urlcolor=DarkBlue, linkcolor=DarkBlue]{hyperref}

\usepackage{microtype} % For better typography

% Configure font settings
\renewcommand{\rmdefault}{ppl} % Use Palatino font
\renewcommand{\sfdefault}{phv} % Use Helvetica font for sans-serif text
\renewcommand*{\namefont}{\fontsize{26}{18}\mdseries}

% Configure microtype
\microtypesetup{expansion=false}

% Load sensitive information
\input{../../personal_info.tex}

% %--------------------------

\begin{document}
\makecvtitle
Hello, I am writing to apply for the position as Data Scientist in Danske Bank's AI Centre of Excellence. With a Master's degree in data science and applied mathematics, and 6 years of professional experience working with machine learning, I am excited to keep learning and to help build impactful and responsible AI solutions at scale.

\hspace*{2em}
Directly after my studies I continued work at RaySearch Laboratories in Stockholm with whom I had written my Master's thesis. My experience at RaySearch as a Data Science Researcher left a strong, long-lasting impression. I developed ML-based methods for radiotherapy planning of cancer treatment. The work was challenging and rewarding, and involved building custom autoencoders for computer vision. Though I had to leave Stockholm in 2021 to move to Copenhagen, I have kept on working with machine learning since.

\hspace*{2em}
In Copenhagen I have worked with data science as a consultant at Valcon, where I built real-time ML inference pipelines for financial data, and at Signum Life Science, where I have owned, extended, and maintained price forecasting models and other deep learning systems. These experiences have given me a solid foundation in applying machine learning to real-world problems, and have honed my skills in building robust and scalable systems.

\hspace*{2em}
I have also architected and led the development of deep learning based systems from the ground up and have in my own time developed an end-to-end machine learning pipeline for multi-modal "shop-the-look" classification for e-commerce in the fashion industry. These projects gave me practical experience with the entire machine learning lifecycle, from data collection and preprocessing to model training and deployment. The shop-the-look classifier incorporates a custom built chrome extension and a FastAPI backend to display results in real-time in your web-browser.

\hspace*{2em}
Beyond model development, I have organised company-wide hackathons, mentored colleagues, and helped shape internal standards for scalable ML tooling. I deeply enjoy sharing knowledge and fostering a culture of learning within teams is very important to me.

\hspace*{2em}
Outside of work, I fill my free time with designing furniture, woodworking, coding, 3D-printing, climbing, road biking, ultimate frisbee, and board games, activities that keep my hands and mind sharp. I thoroughly enjoy picking up new skills and am self taught in all my hobbies.

\vspace{8 mm}
I hope to hear back from you soon. Regards, 

\vspace{3 mm} 
Ivar Cashin Eriksson.

\end{document}